\documentclass[10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\setlist[itemize]{noitemsep, topsep=0pt, left=1em}
\titleformat{\section}{\bfseries\large}{}{0em}{}
\titleformat{\subsection}{\bfseries\normalsize}{}{0em}{}

\pagestyle{empty}
\begin{document}

\section*{Cue Card 1: Hook – Contracts You Didn't Read (5 mins)}
\textbf{Say:}
\begin{itemize}
  \item "You’ve all checked a box agreeing to Terms and Conditions—and skipped reading it. That’s a contract."
  \item "CS uses contracts too. A function contract says: input, output, and purpose."
\end{itemize}
\textbf{Quick Write:} What’s a contract in computer science?
\textbf{Meta:} Students already intuit systems—they’re just not used to formalizing them.

\section*{Cue Card 2: Primer – Known Functions (5 mins)}
\textbf{Model:}
\begin{itemize}
  \item \texttt{print()} → input: string → output: text
  \item \texttt{search("boba")}: input: string → output: location list
\end{itemize}
\textbf{Ask:} What's the contract for your PB\&J or cypher activity?
\textbf{Meta:} Abstraction begins with recognizing structure in actions.

\section*{Cue Card 3: Contract Hunt – Abstract Analysis (15 mins)}
\textbf{Directions:}
\begin{itemize}
  \item Underline input, circle output, bracket purpose.
  \item Fill out contract table in own words.
\end{itemize}
\textbf{While Circulating, Ask:}
\begin{itemize}
  \item "Is that really the input—or just context?"
  \item "What does this system assume?"
\end{itemize}
\textbf{Meta:} All systems encode assumptions. Good design surfaces them.

\section*{Cue Card 4: Whole-Class Share + Pixel Example (8 mins)}
\textbf{Board Contract Example:} Choose 1 abstract. Build contract live.
\begin{itemize}
  \item Invite revisions. Prompt: "Does this work for everyone?"
\end{itemize}
\textbf{Anchor Example – MTA + Google Pixel:}
\begin{itemize}
  \item Sensors detect vibration → ML flags defects → Alert
  \item Limitations: sensor access, signal quality, human response
\end{itemize}
\textbf{Bridge Line:} "What problems could we solve, if we had the right data?"

\section*{Cue Card 5: Invent-a-Tool Design (7 mins)}
\textbf{Prompt:}
\begin{itemize}
  \item "Think of something broken around you—school, commute, systems."
  \item "Define the contract: Input / Output / Purpose / Risks"
\end{itemize}
\textbf{Support Questions:}
\begin{itemize}
  \item What’s the input? What could go wrong?
  \item Who benefits? Who’s left out?
\end{itemize}
\textbf{Meta:} Not “make an app”—see the system, name the gap.

\section*{Cue Card 6: GPT + Exit Ticket (3–5 mins)}
\textbf{Say:}
\begin{itemize}
  \item "GPT can reflect what’s been said—it can’t sense your world."
  \item "You’re learning to build the tools that don’t exist yet."
\end{itemize}
\textbf{Exit Prompt:} Why do we define contracts before we code?
\textbf{Meta:} Code without clarity is just noise. Contract is clarity.

\end{document}
