\documentclass[12pt]{article}
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{0pt}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\section*{Hidden Figures in Computer Science and Mathematics}

These individuals have made profound contributions to computing, mathematics, and education—often without receiving the recognition they deserve. Their stories provide historical grounding for culturally responsive pedagogy and meaningful representation in STEM.

\subsection*{Dr. Marsha R. Williams}
\textbf{First Black woman in the U.S. to earn a PhD in Computer Science (1982)}\\
Worked in educational technology and computer-based learning systems. Advocate for equity in CS access and opportunity.

\subsection*{Dr. Valerie Taylor}
High-performance computing researcher and equity leader. CEO of CMD-IT, an organization that promotes inclusion in computing for minorities and people with disabilities.

\subsection*{Evelyn Boyd Granville}
\textbf{Second Black woman to earn a PhD in mathematics in the U.S. (1949)}\\
Worked on NASA space missions including Mercury and Apollo. Believed deeply in math as a civil rights tool and spent decades teaching and mentoring.

\subsection*{Dr. Gladys West}
Mathematician whose modeling work enabled GPS. Developed complex geodesy equations that underlie modern navigation systems.

\subsection*{Dorothy Vaughan}
Pioneering mathematician and programmer. Led a team of Black women programmers at NASA. Mastered and taught FORTRAN during NASA’s digital transition.

\subsection*{Melba Roy Mouton}
NASA program manager and head mathematician. Her leadership helped compute vital spacecraft trajectories and analyze satellite data.

\subsection*{Dr. Kimberly Bryant}
Electrical engineer and founder of \textbf{Black Girls CODE}. Built an organization to teach programming and robotics to Black girls across the U.S.

\subsection*{Annie Easley}
Rocket scientist, mathematician, and computer programmer. Contributed code to energy systems and hybrid vehicle development.

\subsection*{Mary Jackson}
NASA’s first Black female engineer. Fought for integrated training opportunities and later worked to support other women in STEM roles.

\subsection*{Dr. Lisa Gelobter}
Software engineer behind early animation tools (including the GIF). Worked on Shockwave, Hulu, and led tech for HealthCare.gov recovery. Advocate for inclusive innovation.

\end{document}
