\documentclass[12pt]{article}
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{0pt}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\section*{Function Scenario Creator}

\textbf{Name:} \underline{\hspace{2.5in}} \hfill \textbf{Date:} \underline{\hspace{1in}} \\[1em]

\textbf{Instructions:} In this activity, you'll write your own real-world scenario that can be modeled with a function. You're not modeling a "thing"—you're modeling a \textit{problem}. Focus on what changes, what stays the same, and who is using the function.

\vspace{1em}

\textbf{Step 1: Describe the Scenario}

Write a short description of a real or realistic situation that could be modeled with a function. It can be personal, school-related, fictional, or practical.

\vspace{2em}
\framebox[\textwidth]{
  \parbox[t]{0.95\textwidth}{
    \vspace{1.5em}
    \textit{Example: A bodega sells sandwiches for \$6 each. I want to track how many sandwiches I can buy with a given amount of money.}
    
    \vspace{3em}
    \textbf{Your Scenario:} \\[1em]
    \rule{\textwidth}{0.5pt} \\[1em]
    \rule{\textwidth}{0.5pt} \\[1em]
    \rule{\textwidth}{0.5pt}
  }
}

\vspace{2em}

\textbf{Step 2: Define the Function Details}

\begin{itemize}
  \item \textbf{What is the input? (Domain)} \\[0.5em]
  \underline{\hspace{\textwidth}}\\[1em]

  \item \textbf{What is the output? (Range)} \\[0.5em]
  \underline{\hspace{\textwidth}}\\[1em]

  \item \textbf{What is the purpose of this function? (Why would someone use it?)} \\[0.5em]
  \underline{\hspace{\textwidth}}\\[1em]

  \item \textbf{What type of function would model this?} (Circle one) \\[0.5em]
  \textcircled{\scriptsize L} Linear \quad
  \textcircled{\scriptsize Q} Quadratic \quad
  \textcircled{\scriptsize E} Exponential \quad
  \textcircled{\scriptsize P} Piecewise \quad
  \textcircled{\scriptsize A} Absolute Value \quad
  \textcircled{\scriptsize O} Other: \underline{\hspace{1.5in}}

\end{itemize}

\vspace{2em}

\textit{Optional:} Sketch a quick graph of what this function might look like. What’s the shape? Where does it start? Does it increase, decrease, level off?

\vspace{2em}
\framebox[\textwidth]{
  \parbox[t]{0.95\textwidth}{
    \vspace{4em}
    \hfill \textit{Graph Sketch (optional)}
    \vspace{2em}
  }
}

\end{document}
